Bayesian Nonparametric Motor-skill Representations \\ for Efficient Learning of Robotic Clothing Assistance

### 2016-12-05 Poster/poster.tex
[minor] edit template file with current content

\begin{column}{.02\linewidth}\end{column}

\begin{column}{0.47\linewidth}

\begin{block}{Introduction}

\begin{center}
\textbf{Objective}: Robotic Clothing Assistance is a challenging problem involving \emph{interaction with Human and Clothing material}. In this study, we propose a method for the realtime estimation of the Human-Cloth topological relationship using a depth sensor.
\end{center}

\begin{column}{0.55\linewidth}

~\\
Tamei et. al.[1] developed clothing assistance robot to perform T-shirt clothing task:\\~\\
\begin{itemize}
\item \textbf{Reinforcement Learning} scheme used to acquire motor skills for cloth handling.\\~\\
\item \textbf{Low dimensional represetations} of state and policy used to ensure fast learning time.
\end{itemize}

@@

\begin{column}{0.45\linewidth}

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{mannequin.png}
\end{figure}

@@

\begin{column}{0.47\linewidth}

\begin{block}{Problem Decription}

\begin{column}{0.5\linewidth}
\textbf{Topology Coordinates}[2] represents interaction between two curves using low dimensional variables:

\begin{itemize}
\item \textbf{Writhe}, $w \in \mathbb{R}$
\vspace{3mm}
\item \textbf{Center}, $\text{c} = [c_1,c_2] \in \mathbb{R}^2$
\vspace{3mm}
\item \textbf{Density}, $d \in \mathbb{R}$
\end{itemize}

\vspace{3mm}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{humancloth.pdf}
\end{figure}

\begin{column}{0.5\linewidth}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{topology.png}
\end{figure}

\vspace{3mm}

\centering \textbf{Human-Cloth relationship} low dimensionally represented using topology coordinates:

\begin{itemize}
\item T-shirt collar and Mannequin's Head
\vspace{2mm}
\item T-shirt collar and Mannequin's Body
\vspace{2mm}
\item T-shirt sleeve and Mannequin's Shoulder
\end{itemize}

\begin{column}{.02\linewidth}\end{column}

\begin{column}{0.02\linewidth}\end{column}

\begin{column}{0.96\linewidth}

\begin{alertblock}{Proposed Method}

\begin{column}{0.24\linewidth}

\centering \textbf{Experimental Setup}

\begin{itemize}
\item Human-Cloth relationship observed using \textbf{Kinect depth sensor}.\\~\\
\item \textbf{Color markers} used on T-shirt and Mannequin to ensure robust estimation.
\end{itemize}

\vspace{6mm}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{setup.png}
\end{figure}

\begin{column}{0.48\linewidth}

\centering \textbf{Proposed Method}

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=0.22\textheight]{method.pdf}
\end{figure}

\begin{column}{0.24\linewidth}

\centering \textbf{T-shirt state estimation}

\vspace{3mm}

\begin{itemize}
\item T-shirt collar and sleeve shape compactly represented using \textbf{Ellipses}.\\~\\
\item Generic 3D conic fitting approach proposed Shakarji et. al.~\cite{ellipse} used for this purpose.
\end{itemize}

\vspace{3mm}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{collarestimates.pdf}
\end{figure}

@@

\centering \textbf{Robustness of Topology Space to Measurement Noise}\\
\vspace{3mm}
\centering Robustness evaluated by comparing rewards obtained in \emph{Cartesian} and \emph{Topological} space.

>>>>

\begin{columns}[t]
  \begin{column}{.02\linewidth}\end{column}

  \begin{column}{0.47\linewidth}
    \begin{block}{Introduction}
      \begin{center}
        \textbf{Abstract}: Motor-skill learning for complex robotic tasks is a challenging problem due to the high task variability. Robotic clothing assistance is one such challenging problem that can greatly improve the quality-of-life for the elderly and disabled. In this study, we propose a data-efficient representation to encode task specific motor-skills of the robot using Bayesian nonparametric latent space learning. We implement our framework in a practical setting with a dual-arm robot performing clothing assistance tasks. We demonstrate that performing motor-skills learning in such task specific latent spaces outperforms learning in the high-dimensional joint configuration space of the robot. Furthermore, our framework can also be used as a tool for learning from demonstration to impart novel skills to the robot.
      \end{center}
    \end{block}
  \end{column}

  \begin{column}{0.47\linewidth}
    \begin{block}{Problem Decription}

    \end{block}
  \end{column}

  \begin{column}{.02\linewidth}\end{column}
\end{columns}

\begin{columns}[t]
  \begin{column}{0.02\linewidth}\end{column}

  \begin{column}{0.96\linewidth}
    \begin{alertblock}{Motor-skill Representations in Latent Spaces}
      \begin{columns}[t]
        \begin{column}{0.24\linewidth}
          \centering \textbf{Learning from Demonstration}

@@

        \begin{column}{0.48\linewidth}
          \centering \textbf{Proposed Framework}

@@

        \begin{column}{0.24\linewidth}
          \centering \textbf{Reinforcement Learning Formulation}

        \end{column}
      \end{columns}
    \end{alertblock}
  \end{column}

  \begin{column}{0.02\linewidth}\end{column}
\end{columns}

@@

\centering \textbf{}\\
\vspace{3mm}
\centering Robustness evaluated by comparing rewards obtained in \emph{Cartesian} and \emph{Topological} space.
